---
title: "FBS analysis"
output:
  html_notebook:
    code_folding: hide
    toc: yes
---

```{r setup,echo=F}
knitr::opts_knit$set(root.dir = here::here())
library(here)
source(here("code/common_basis.R"), local = knitr::knit_global())
library(tidyverse)
library(gghsci)
library(gt)
p <- function(number) {
  return(format(number, scientific = FALSE, big.mark = ","))
}
pp <- function(percentage, accuracy = 0.01) {
  return(scales::percent(percentage, accuracy = accuracy))
}
```

```{r}
vd17_contributors1_a_local <-vd17_contributors1_a %>%
  collect()
vd17_contributors2_a_local <-vd17_contributors2_a %>%
  collect()
vd17_contributors3_a_local <-vd17_contributors3_a %>%
  collect()
vd17_contributors4_a_local <-vd17_contributors4_a %>%
  collect()

vd17_contributors_a_local <-rbind(vd17_contributors1_a_local,vd17_contributors2_a_local,vd17_contributors3_a_local,vd17_contributors4_a_local)
```

```{r}
vd17_dedicatees1_a_local <-vd17_dedicatees1_a %>%
  collect()
vd17_dedicatees2_a_local <-vd17_dedicatees2_a %>%
  collect()
vd17_dedicatees3_a_local <-vd17_dedicatees3_a %>%
  collect()

vd17_dedicatees_a_local <-rbind(vd17_dedicatees1_a_local,vd17_dedicatees2_a_local,vd17_dedicatees3_a_local)

```


```{r}
vd17_contributors_dedicatees <- rbind(vd17_contributors_a_local,vd17_dedicatees_a_local)

vd17_contributors_dedicatees <- vd17_contributors_dedicatees %>%
  distinct(record_number)

fbs_record_numbers_gnd_local <- fbs_links_a %>%
  collect()%>%
  select(record_number,6)

colnames(fbs_record_numbers_gnd_local) <- c('record_number','GND')

fbs_record_numbers_gnd_local <- fbs_record_numbers_gnd_local %>%
  distinct(record_number,GND)

fbs_contributors_dedicatees <- fbs_record_numbers_gnd_local %>%
  inner_join(vd17_contributors_dedicatees, by = c("record_number"))

vd17_normalized_years_local <- vd17_normalized_years_a %>%
  collect()

```

# FBS publications by year for members (not contributors_dedicatees)
The below plot depicts the number of publications (plus cumulative distribution) by FBS members by year.

```{r}
publications_fbs <- fbs_record_numbers_gnd_local %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)

publications_fbs <- publications_fbs[!publications_fbs$GND %in% fbs_contributors_dedicatees$GND, , drop = FALSE]

pub_fbs <-publications_fbs %>%
  group_by(normalized_year) %>%
  summarize(records = n_distinct(record_number), .groups = "drop") %>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))

  ggplot(pub_fbs,aes(x=normalized_year, y=records, color = phase)) + 
  geom_step()+
  xlab("Year") + ylab("Number of publications")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

cumulative_frequencies_pub <- pub_fbs %>% 
  arrange(normalized_year) %>% 
  mutate(cum_frequency=cumsum(records))%>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))


ggplot(cumulative_frequencies_pub, aes(x=normalized_year, y=cum_frequency)) +
  geom_step()+
  xlab("Year") + ylab("Publications (cumulative distribution)")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

```
# FBS publications by year for members (all)
The below plot depicts the number of publications (plus cumulative distribution) by FBS members by year.

```{r}
publications_fbs_all <- fbs_record_numbers_gnd_local %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)

pub_fbs_all <-publications_fbs_all %>%
  group_by(normalized_year) %>%
  summarize(records = n_distinct(record_number), .groups = "drop") %>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))

  ggplot(pub_fbs_all,aes(x=normalized_year, y=records, color = phase)) + 
  geom_step()+
  xlab("Year") + ylab("Number of publications (all)")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

cumulative_frequencies_pub_all <- pub_fbs_all %>% 
  arrange(normalized_year) %>% 
  mutate(cum_frequency=cumsum(records))%>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))


ggplot(cumulative_frequencies_pub_all, aes(x=normalized_year, y=cum_frequency)) +
  geom_step()+
  xlab("Year") + ylab("Publications (all-cumulative distribution)")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

```
# FBS members by year
The below plot depicts the number of members of FBS by year.
```{r}
members_fbs <- fbs_record_numbers_gnd_local %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)

members_fbs <- members_fbs[!members_fbs$GND %in% fbs_contributors_dedicatees$GND, , drop = FALSE]

mem_fbs <-members_fbs %>%
  group_by(normalized_year) %>%
  summarize(records = n_distinct(GND), .groups = "drop") %>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))

  ggplot(mem_fbs,aes(x=normalized_year, y=records, color = phase)) + 
  geom_step()+
  xlab("Year") + ylab("Number of members")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```


# FBS members by year (all)
The below plot depicts the number of members of FBS by year.
```{r}
members_fbs_all <- fbs_record_numbers_gnd_local %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)

mem_fbs_all <-members_fbs_all %>%
  group_by(normalized_year) %>%
  summarize(records = n_distinct(GND), .groups = "drop") %>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))

  ggplot(mem_fbs_all,aes(x=normalized_year, y=records, color = phase)) + 
  geom_step()+
  xlab("Year") + ylab("Number of members (all)")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

```


# FBS genres by year
The below plot depicts the top genre of FBS publications by year.


```{r}
vd17_genres_local <- vd17_genres_a %>%
  collect()

genres_fbs <- fbs_record_numbers_gnd_local %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)%>%
  left_join(vd17_genres_local, by = c("record_number"))

genres_fbs <- genres_fbs[!genres_fbs$GND %in% fbs_contributors_dedicatees$GND, , drop = FALSE]

phase_genres_fbs <- genres_fbs%>%
  select(record_number,normalized_year,genre)%>%
  distinct(record_number,normalized_year,genre)%>%
  na.omit(genres_fbs)%>%
  group_by(normalized_year) %>%
  count(genre)%>%
  arrange(desc(n))%>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))

phase_genres_fbs %>% write_csv(here("fbs_genres.csv"))

phase_genres_fbs%>%
  slice(1:1)%>%
  ggplot(aes(x=normalized_year,y=n,fill=genre))+
  geom_col()+
  xlab("Year") + ylab("Top genre of FBS by year")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
  theme(legend.position="bottom",
        legend.key.width=unit(0.15, "cm"))+
  geom_text(aes(label = n), color = "black", size = 1, position = position_stack(vjust = 0.9)) 
```

# FBS genres by year (all)
The below plot depicts the top genre of FBS publications by year.

```{r}

genres_fbs_all <- fbs_record_numbers_gnd_local %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)%>%
  left_join(vd17_genres_local, by = c("record_number"))

phase_genres_fbs_all <- genres_fbs_all%>%
  select(record_number,normalized_year,genre)%>%
  distinct(record_number,normalized_year,genre)%>%
  na.omit(genres_fbs_all)%>%
  group_by(normalized_year) %>%
  count(genre)%>%
  arrange(desc(n))%>%
  mutate(phase = case_when(
    normalized_year < 1617 ~ "< 1617",
    normalized_year >= 1617 & normalized_year <= 1650 ~ "phase 1",
    normalized_year >= 1651 & normalized_year <= 1667 ~ "phase 2",
    normalized_year >= 1668 & normalized_year <= 1682 ~ "phase 3",
    normalized_year > 1682 ~ "> 1682"
  ))

phase_genres_fbs_all %>% write_csv(here("fbs_genres_all.csv"))

phase_genres_fbs_all%>%
  slice(1:1)%>%
  ggplot(aes(x=normalized_year,y=n,fill=genre))+
  geom_col()+
  xlab("Year") + ylab("Top genre of FBS by year (all)")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
  theme(legend.position="bottom",
        legend.key.width=unit(0.15, "cm"))+
  geom_text(aes(label = n), color = "black", size = 1, position = position_stack(vjust = 0.9)) 
```

