---
title: "FBS analysis"
output:
  html_notebook:
    code_folding: hide
    toc: yes
---

```{r setup,echo=F}
knitr::opts_knit$set(root.dir = here::here())
library(here)
source(here("code/common_basis.R"), local = knitr::knit_global())
library(tidyverse)
library(gghsci)
library(gt)
p <- function(number) {
  return(format(number, scientific = FALSE, big.mark = ","))
}
pp <- function(percentage, accuracy = 0.01) {
  return(scales::percent(percentage, accuracy = accuracy))
}
```

# Identifying rescue values
```{r}
list_rescue <- c("Palmen Orden","Palmen-Orden","Palmenorden","Fruchtbringend","Frucht-bringend","Frucht Bringend","Die deutsche Akademie des 17. Jahrhunderts - Fruchtbringende Gesellschaft","Akademie des 17. Jahrhunderts","Akademie des Siebzehnten Jahrhunderts","Deutsche Akademie des Siebzehnten Jahrhunderts","Deutsche Akademie des 17. Jahrhunderts","Palmenorden","Akademie des Siebzehnten Jahrhunderts","Akademie des 17. Jahrhunderts","Societas Fructifera","Frugtbringende Selskab","Fruitbearing Society","Sociedad Fructífera","Société des Fructifiants","Ordre du Palmier","Società dei Carpofori","Towarzystwo Owocodajne","Komunitas Fruitbearing","Плодоносное общество","丰收学会")

vd17_rescue <- vd17_a %>%
  mutate(value = str_replace_all(value, sql("CHR(0)"), "_")) %>%
  collect()%>%
  filter(grepl(paste(list_rescue, collapse="|"), value))%>%
  mutate(rescue_value=value,rescue_field=field_code)%>%
  select(record_number,rescue_value,rescue_field)%>%
  distinct()

```

```{r}
vd17_rescue_additional_field<-vd17_a %>% filter(field_code %in% c("029A","029F","029G","028G","037A"), subfield_code %in% c("a","B","P"))%>%select(record_number,resuce_additional_field=value)

vd17_a_rescue <- vd17_rescue %>%
  copy_to_a(con,temporary=TRUE,overwrite=TRUE)%>%
  left_join(vd17_rescue_additional_field,by=c("record_number"))%>%
  left_join(vd17_id_a,by=c("record_number"))%>%
  collect()%>%
  distinct()
```

```{r}
all_match <- read.csv(here("all_match.csv"))
all_match <- select (all_match, -c('X','full_name_vd17','normalized_year','field_number'))
all_match_subset <-  all_match%>%
  filter(
    field_code %in% c("028B", "028C"), 
    grepl(paste(c("Widmungsempfänger","Widmungsempfängerin"),collapse="|"), role2))
```

```{r}
all_match_subset <- select(all_match_subset,-c('role'))
```


# Joining vd17_id with fbs_links_of_interest 
```{r}
fbs_local <- fbs_links_a %>%
  inner_join(fbs_metadata_a %>% select(GND,Member_number_new,First_name_new,Last_name_new,Society_name,DOB,DOD) %>% mutate(GND = str_c("gnd/", GND))) %>%
 inner_join(vd17_id_a) %>%
  mutate(member_number=Member_number_new,first_name=First_name_new,last_name=Last_name_new)%>%
  collect()

fbs_local <- select (fbs_local, c('record_number','vd17_id','member_number','first_name', 'last_name','role2','role','field_code'))

fbs_dedicatees_subset <-  fbs_local%>%
  filter(
    field_code %in% c("028B", "028C"), 
    grepl(paste(c("Widmungsempfänger","Widmungsempfängerin"),collapse="|"), role2))

```

```{r}
fbs_dedicatees_subset <- select(fbs_dedicatees_subset,-c('role'))
```

```{r}
fbs_dedicatees_subset_match <- rbind(fbs_dedicatees_subset,all_match_subset)

fbs_dedicatees_subset_match <- fbs_dedicatees_subset_match %>%
  distinct()

fbs_rescue <- fbs_dedicatees_subset_match %>%
  merge(vd17_a_rescue, by=c("record_number","vd17_id"),all=TRUE)%>%
  distinct()
```

# Creating local tables of vd17 normalized years, genres, languages, id and title.
```{r}
vd17_normalized_years_local <- vd17_normalized_years_a %>%
  collect()
genre_list2 <- c("Educational","Schul- und Hochschulschriften","Hochschulschrift","Dissertation","Dissertation:theol.","Dissertation:med.","Dissertation:jur.","Dissertation:phil.","Dissertationensammlung","Matrikel","Universitätsprogramm","Vorlesung","Vorlesungsverzeichnis","Jugendsachbuch","Rechenbuch","Schulbuch","Fibel","Lesebuch","Schulprogramm","Governmental","Amtsdruckschrift","Edikt","Gesetz","Gesetzesammlung","Kapitulation","Mandat","Privileg","Richtlinie","Verordnung","Vertrag","Other Governmental and Institutional","Regesten","Urkundenbuch","Judicial","Legal","Entscheidungssammlung","Fallsammlung","Konsiliensammlung","Konsilium","Satzung","Religious","Theological","Agende","Beichtspiegel","Bibel","Brevier","Gebet","Katechismus","Missale","Psalter","Rituale","Business","Mercantile","Anzeige","Subskriptionsanzeige","Meßrelation","Subskribentenliste","Verkaufskatalog","Antiquariatskatalog","Auktionskatalog","Buchhandelskatalog","Meßkatalog","Military","Festungsbau","Kriegskunde","General Works","Bericht","Brief","Briefsammlung","Regelsammlung","Statistik","Streitschrift","Streitschrift:polit.","Streitschrift:jur.","Streitschrift:theol.")

vd17_parts_of_multipart_works <- vd17_parts_of_multipart_works_a%>%
  collect()%>%
  mutate(multipart="multipart")

vd17_genres_local <- vd17_genres_a %>%
  collect()%>%
  filter(!(a %in% c(genre_list2)))%>%
  mutate(genre_full=a)%>%
  select(record_number,genre_full)


vd17_normalized_langs_local <- vd17_normalized_langs_a %>%
  collect()

vd17_id_local <- vd17_id_a %>%
  collect()

vd17_titles_local <- vd17_a %>%
  filter(field_code %in% c("021A","021G","021M","021N","022A"),subfield_code %in% c("a","d","h"))%>%
  select(record_number,value)%>%
  collect()%>%
  group_by(record_number)%>%
  mutate(combined_all_titles = toString(unique(value)))%>%
  distinct(record_number,combined_all_titles)

vd17_corporate_authors_name <- vd17_a %>%
  filter(field_code %in% c("029A","029F","029G"),subfield_code %in% c("a"))%>%
  mutate(corporate_subfield_code_a=field_code,name_corporate=value)%>%
  select(record_number,corporate_subfield_code_a,name_corporate)%>%
  collect()

vd17_corporate_authors_gnd <- vd17_a %>%
  filter(field_code %in% c("029A","029F","029G"),subfield_code %in% c("7"))%>%
  mutate(corporate_subfield_code_7=field_code,gnd_corporate=value)%>%
  select(record_number,corporate_subfield_code_7,gnd_corporate)%>%
  collect()

vd17_corporate_authors_ppn <- vd17_a %>%
  filter(field_code %in% c("029A","029F","029G"),subfield_code %in% c("9"))%>%
  mutate(corporate_subfield_code_9=field_code,ppn_corporate=value)%>%
  select(record_number,corporate_subfield_code_9,ppn_corporate)%>%
  collect()

vd17_corporate_authors_role <- vd17_a %>%
  filter(field_code %in% c("029A","029F","029G"),subfield_code %in% c("B"))%>%
  mutate(corporate_subfield_code_B=field_code,role_corporate=value)%>%
  select(record_number,corporate_subfield_code_B,role_corporate)%>%
  collect()

vd17_corporate_name_gnd <- merge(vd17_corporate_authors_name,vd17_corporate_authors_gnd, by=c("record_number"),all=TRUE)%>%
  distinct()
vd17_corporate_name_ppn <- merge(vd17_corporate_name_gnd,vd17_corporate_authors_ppn, by=c("record_number"),all=TRUE)%>%
  distinct()
vd17_corporate <- merge(vd17_corporate_name_ppn,vd17_corporate_authors_role, by=c("record_number"),all=TRUE)%>%
  distinct()

vd17_genres_combined <- vd17_genres_local %>%
  group_by(record_number) %>% 
  mutate(combined_all_genres = toString(unique(genre_full)))%>%
  distinct(record_number,combined_all_genres)
```

```{r}
genre_list1_a <- c("Lyrik","Lyric Poetry","Ballade","Elegie","Epigramm","Epikedeion","Figurengedicht","Gesangbuch","Lied","Kirchenlied","Liedersammlung")
genre_list1_b <- c("Drama","Theatre","Fastnachtspiel","Komödie","Märtyrerdrama","Schauspiel","Schwank","Tragödie")
genre_list1_c <- c("Epik","Prose","Anekdote","Autobiographie","Biographie","Epos","Erlebnisbericht","Erzählung","Erzählsammlung","Fabel","Märchen","Novelle","Reisebericht","Roman","Sage","Satire","Tagebuch","Verserzählung")
genre_list1_d <- c("Other Literature Related","Content Related","Schäferdichtung","Libretto","Erotische Literatur","Emblembuch","Porträtwerk","Theaterzettel","Content Neutral","Almanach","Anthologie","Kommentar:lit.","Rezension","Rezensionszeitschrift")
genre_list1_e <- c("Linguistic and Language","Grammatik","Konkordanz","Lexikon","Poetik","Rhetorik","Sprachführer","Wörterbuch","Epistolography","Briefsteller","Formularsammlung","Schreibmeisterbuch")
genre_list1_f <- c("Virtue, Civility and Ethics","Aphorismus","Anstandsliteratur","Enzyklopädie","Frauenliteratur","Fürstenspiegel","Hausväterliteratur","Jugendbuch","Kochbuch","Moralische Wochenschrift","Spiel","Sprichwortsammlung","Zitatensammlung")
genre_list1_g <- c("Other Society Related","Gesellschaftschrift","Akademieschrift")
genre_list1_h <- c("Occasional Literature","Funeral Sermons","Leichenpredigt","Leichenpredigtsammlung","Festbeschreibung","Gelegenheitsschrift")
genre_list1_i <- c("German as a scientific language","History, Archaeology and related","Archäologie","Altertumskunde","Chronik","Genealogie","Wappenbuch","Botany, Zoology, Agriculture","Botanik","Gartenbau","Jagdliteratur","Landwirtschaft","Praktik","Pflanzenbuch","Tierbuch","Zoologie","Geography, Geology, Mineralogy, Mining","Bergbau","Geographie","Geologie","Mineralogie","Reiseführer","Topographie","Mathematics, Natural Sciences, Astronomy","Alchemie","Astronomie","Astrologie","Chemie","Physik","Akustik","Magnetismus","Mechanik","Optik","Geometrie","Mathematik","Medicine, Pharmacy","Anatomie","Arzneibuch","Chiromantie","Chirurgie","Gynäkologie","Medizin","Pharmakopöe","Physiognomie","Seuchenschrift","Tiermedizin","Architecture, Music, Arts","Musikbuch","Musiknoten","Architektur","Ornamentstich","Education","Pädagogik")
```

```{r}
translations_notes <- vd17_a %>% 
  mutate(value = str_replace_all(value, sql("CHR(0)"), "_")) %>%
  collect()%>%
  filter(field_code %in% c("037A","046L"), subfield_code=="a")%>%
  mutate(translations_notes=value)%>%
  select(record_number,translations_notes)%>%
  distinct()

vd17_translations_defined <- vd17_normalized_langs_a%>%
  filter(!is.na(original_language),publication_language=="ger")%>%
  left_join(vd17_id_a,by=c("record_number"))%>%
  collect()

vd17_translations_defined_fbs <- vd17_translations_defined%>%
  left_join(translations_notes,by=c("record_number"))%>%
  inner_join(fbs_dedicatees_subset_match,by=c("record_number","vd17_id"))%>%
  select(record_number,translations_notes)
```

```{r}
vd17_id_a_exception <- vd17_id_a %>%
  filter(vd17_id %in% c("23:251993N","23:668151V","12:105826H","1:658583Y","23:292603E","32:723467F","7:685790Q","23:664520X","14:627442V","3:609604X","23:248478N","3:007042D"))%>%
  collect()
  
vd17_corporate_defined <- vd17_a %>% filter(field_code=="029G",str_detect(value,"Frucht"))%>%
mutate(field_code_corporate_exceptions=field_code)%>%
collect()%>%
distinct()

fbs_id_corporate_defined <-vd17_id_a_exception%>% 
  inner_join(vd17_corporate_defined,by=c("record_number"))%>% 
  select(record_number,vd17_id,field_code_corporate_exceptions)
```

# The below plots depicts the genre frequency of FBS publications for Society-related genres.
```{r}

genre_cat1 <- vd17_genres_local%>%
  filter(grepl(paste(c(genre_list1_a,genre_list1_b,genre_list1_c,genre_list1_d,genre_list1_e,genre_list1_f,genre_list1_g,genre_list1_h,genre_list1_i),collapse="|"), genre_full))%>%
  select(record_number,genre_full)

genres_fbs_dedicatees_cat1 <- fbs_rescue %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)%>%
  left_join(vd17_translations_defined_fbs,by=c("record_number"))%>%
  left_join(fbs_id_corporate_defined,by=c("record_number","vd17_id"))%>%
  inner_join(genre_cat1,by = c("record_number"))%>%
  left_join(vd17_titles_local %>% select(record_number,combined_all_titles),by = c("record_number")) %>%
  left_join(vd17_normalized_langs_local%>% select(record_number, publication_language, intermediary_language,original_language), by = c("record_number"))%>%
  left_join(vd17_genres_combined, by=c("record_number"))%>%
  left_join(vd17_parts_of_multipart_works,by=c("record_number"))%>%
  left_join(vd17_corporate, by=c("record_number"))%>%
  select(record_number,normalized_year,vd17_id,combined_all_titles,member_number,first_name,last_name,role2,field_code,original_language,intermediary_language,publication_language,translations_notes,genre_full,combined_all_genres,rescue_value,rescue_field,resuce_additional_field,field_code_corporate_exceptions,corporate_subfield_code_a,corporate_subfield_code_7,corporate_subfield_code_9,corporate_subfield_code_B,name_corporate,gnd_corporate,ppn_corporate,role_corporate,multipart)%>%
  mutate(genre_category = case_when(
    (grepl(paste(genre_list1_a, collapse="|"), genre_full)) ~ "Lyrik/Poetry",
    (grepl(paste(genre_list1_b, collapse="|"), genre_full)) ~ "Drama/Theatre",
    (grepl(paste(genre_list1_c, collapse="|"), genre_full)) ~ "Epik/Prose",
    (grepl(paste(genre_list1_d, collapse="|"), genre_full)) ~ "Other Literature Related",
    (grepl(paste(genre_list1_e, collapse="|"), genre_full)) ~ "Linguistic and Language",
    (grepl(paste(genre_list1_f, collapse="|"), genre_full)) ~ "Virtue, Civility and Ethics",
    (grepl(paste(genre_list1_g, collapse="|"), genre_full)) ~ "Other Society Related",
    (grepl(paste(genre_list1_h, collapse="|"), genre_full)) ~ "Occasional Literature",
    (grepl(paste(genre_list1_i, collapse="|"), genre_full)) ~ "German as a scientific language"
  ))%>%
  distinct()
```

```{r}
genres_number_fbs_cat1 <- genres_fbs_dedicatees_cat1%>%
  select(vd17_id,record_number,normalized_year,genre_full)%>%
  distinct(vd17_id,record_number,normalized_year,genre_full)%>%
  group_by(normalized_year) %>%
  count(genre_full)%>%
  arrange(desc(n))%>%
   mutate(genre_category = case_when(
    (grepl(paste(genre_list1_a, collapse="|"), genre_full)) ~ "Lyrik/Poetry",
    (grepl(paste(genre_list1_b, collapse="|"), genre_full)) ~ "Drama/Theatre",
    (grepl(paste(genre_list1_c, collapse="|"), genre_full)) ~ "Epik/Prose",
    (grepl(paste(genre_list1_d, collapse="|"), genre_full)) ~ "Other Literature Related",
    (grepl(paste(genre_list1_e, collapse="|"), genre_full)) ~ "Linguistic and Language",
    (grepl(paste(genre_list1_f, collapse="|"), genre_full)) ~ "Virtue, Civility and Ethics",
    (grepl(paste(genre_list1_g, collapse="|"), genre_full)) ~ "Other Society Related",
    (grepl(paste(genre_list1_h, collapse="|"), genre_full)) ~ "Occasional Literature",
    (grepl(paste(genre_list1_i, collapse="|"), genre_full)) ~ "German as a scientific language"
  ))%>%
  distinct()


genres_number_fbs_cat1%>%
  ggplot(aes(x=normalized_year,y=n,fill=genre_category))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~genre_category, scales="free")+
  xlab("Year") + ylab("FBS-Dedicatees-Society-related genres")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

genres_number_fbs_cat1%>%
  ggplot(aes(x=normalized_year,y=n,fill=genre_category))+
  geom_col(width=1,position='fill')+
  labs(fill=NULL)+
  xlab("Year") + ylab("FBS-Dedicatees-Society-related genres")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  scale_y_continuous(labels=scales::percent_format(accuracy=1),breaks = seq(0, 1, by = 0.1)) +
  theme_hsci_discrete()+
  theme(legend.position = "bottom")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```

# Genre frequency of FBS publications by year per author for Society-related genres.
```{r}
genres_members_fbs_cat1 <- genres_fbs_dedicatees_cat1%>%
  select(vd17_id,record_number,normalized_year,member_number,genre_full)%>%
  distinct(vd17_id,record_number,normalized_year,member_number,genre_full)%>%
  group_by(normalized_year,member_number) %>%
  count(genre_full)%>%
  arrange(desc(n))%>%
  mutate(genre_category = case_when(
    (grepl(paste(genre_list1_a, collapse="|"), genre_full)) ~ "Lyrik/Poetry",
    (grepl(paste(genre_list1_b, collapse="|"), genre_full)) ~ "Drama/Theatre",
    (grepl(paste(genre_list1_c, collapse="|"), genre_full)) ~ "Epik/Prose",
    (grepl(paste(genre_list1_d, collapse="|"), genre_full)) ~ "Other Literature Related",
    (grepl(paste(genre_list1_e, collapse="|"), genre_full)) ~ "Linguistic and Language",
    (grepl(paste(genre_list1_f, collapse="|"), genre_full)) ~ "Virtue, Civility and Ethics",
    (grepl(paste(genre_list1_g, collapse="|"), genre_full)) ~ "Other Society Related",
    (grepl(paste(genre_list1_h, collapse="|"), genre_full)) ~ "Occasional Literature",
    (grepl(paste(genre_list1_i, collapse="|"), genre_full)) ~ "German as a scientific language"
  ))%>%
  distinct()

```

```{r}
genre_list3_a <- c("Religion","Theology and related","Ars moriendi","Erbauungsliteratur","Freimaurerliteratur","Gebetbuch","Heiligenvita","Jesuitendrama","Judaicum","Legende","Predigt","Perioche","Predigtsammlung","Totentanz","Ordensliteratur")


genre_list3_b <- c("General works","Adressbuch","Anleitung","Atlas","Bibliographie","Buchbinderanweisung","Bücheranzeige","Einführung","Führer","Handbuch","Itinerar","Kalender","Karte","Katalog","Konkordanz","Musterbuch","Plan","Rede","Panegyrikos","Ratgeber","Ortsverzeichnis","Preisschrift","Regelsammlung","Traktat","Trivialliteratur","Kolportageliteratur","Volksschrifttum","Volksbuch","Kommentar:hist.","Kommentar:jur.","Kommentar:pol.", "Kommentar:theol.")


genre_list3_c <- c("Formats","Einblattdruck","Flugschrift","Tabelle","Zeitung","Zeitschrift")

#"no genre category" should be included in neutral part
```
# The below plots depicts the genre frequency of FBS publications for Neutral genres.
```{r}

vd17_genres_local_cat3 <- vd17_genres_local%>%
  filter(grepl(paste(c(genre_list3_a,genre_list3_b,genre_list3_c),collapse="|"), genre_full))

genres_fbs <- fbs_rescue %>%
  left_join(vd17_genres_local, by = c("record_number"))%>%
  select(record_number,genre_full)

fbs_without_genre <- genres_fbs%>%
  filter(is.na(genre_full))

genre_na_cat3 <- rbind(fbs_without_genre,vd17_genres_local_cat3)

genres_fbs_dedicatees_cat3 <- fbs_rescue %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year)==4)%>%
  inner_join(genre_na_cat3,by = c("record_number"))%>%
  left_join(vd17_titles_local %>% select(record_number,combined_all_titles),by = c("record_number")) %>%
  left_join(vd17_normalized_langs_local%>% select(record_number, publication_language, original_language), by = c("record_number"))%>%
  left_join(vd17_genres_combined, by=c("record_number"))%>%
  left_join(vd17_parts_of_multipart_works,by=c("record_number"))%>%
  left_join(vd17_corporate, by=c("record_number"))%>%
  select(record_number,normalized_year,vd17_id,combined_all_titles,member_number,first_name,last_name,role2,field_code,original_language,publication_language,genre_full,combined_all_genres,rescue_value,rescue_field,resuce_additional_field,corporate_subfield_code_a,corporate_subfield_code_7,corporate_subfield_code_9,corporate_subfield_code_B,name_corporate,gnd_corporate,ppn_corporate,role_corporate,multipart)%>%
  mutate(genre_category = case_when(
    (grepl(paste(genre_list3_a, collapse="|"), genre_full)) ~ "Religion/Theology and related",
    (grepl(paste(genre_list3_b, collapse="|"), genre_full)) ~ "General works",
    (grepl(paste(genre_list3_c, collapse="|"), genre_full)) ~ "Formats"))%>%
  distinct()
```

```{r}
genres_number_fbs_cat3 <- genres_fbs_dedicatees_cat3%>%
  select(vd17_id,record_number,normalized_year,genre_full)%>%
  distinct(vd17_id,record_number,normalized_year,genre_full)%>%
  group_by(normalized_year) %>%
  count(genre_full)%>%
  arrange(desc(n))%>%
   mutate(genre_category = case_when(
    (grepl(paste(genre_list3_a, collapse="|"), genre_full)) ~ "Religion/Theology and related",
    (grepl(paste(genre_list3_b, collapse="|"), genre_full)) ~ "General works",
    (grepl(paste(genre_list3_c, collapse="|"), genre_full)) ~ "Formats"))%>%
  distinct()


genres_number_fbs_cat3%>%
  ggplot(aes(x=normalized_year,y=n,fill=genre_category))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~genre_category, scales="free")+
  xlab("Year") + ylab("FBS-Dedicatees-Neutral/NA genres")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  theme_hsci_discrete()+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

genres_number_fbs_cat3%>%
  ggplot(aes(x=normalized_year,y=n,fill=genre_category))+
  geom_col(width=1,position='fill')+
  labs(fill=NULL)+
  xlab("Year") + ylab("FBS-Dedicatees-Neutral/NA genres")+
  scale_x_continuous(breaks = seq(1000, 2000, by = 5))+
  scale_y_continuous(labels=scales::percent_format(accuracy=1),breaks = seq(0, 1, by = 0.1)) +
  theme_hsci_discrete()+
  theme(legend.position = "bottom")+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```

# Genre frequency of FBS publications by year per author for Neutral genres.
```{r}
genres_members_fbs_cat3 <- genres_fbs_dedicatees_cat3%>%
  select(vd17_id,record_number,normalized_year,member_number,genre_full)%>%
  distinct(vd17_id,record_number,normalized_year,member_number,genre_full)%>%
  group_by(normalized_year,member_number) %>%
  count(genre_full)%>%
  arrange(desc(n))%>%
  mutate(genre_category = case_when(
    (grepl(paste(genre_list3_a, collapse="|"), genre_full)) ~ "Religion/Theology and related",
    (grepl(paste(genre_list3_b, collapse="|"), genre_full)) ~ "General works",
    (grepl(paste(genre_list3_c, collapse="|"), genre_full)) ~ "Formats"))%>%
  distinct()
```

# Solving the Token_authontication problem
```{r}
options(gargle_oauth_cache = ".secrets")

# Authenticate manually

gs4_auth()

# If successful, the previous step stores a token file.

# Check that a file has been created with:

list.files(".secrets/")

# Check that the non-interactive authentication works by first deauthorizing:

gs4_deauth()

# Authenticate using token. If no browser opens, the authentication works.

gs4_auth(cache = ".secrets", email = "narges.azizifard@gmail.com")
```

# Creating the google spreadsheet
```{r}

 genre_fbs_cat1_link <- genres_fbs_dedicatees_cat1%>%
     mutate(vd17_id=gs4_formula(str_c('=HYPERLINK("https://kxp.k10plus.de/DB=1.28/CMD?ACT=SRCHA&IKT=8079&TRM=%27',vd17_id,'%27","',vd17_id,'")')))
my_data_frames_1 <- list(genre_fbs_cat1_link,genres_number_fbs_cat1,genres_members_fbs_cat1)

genre_fbs_cat3_link <- genres_fbs_dedicatees_cat3%>%
     mutate(vd17_id=gs4_formula(str_c('=HYPERLINK("https://kxp.k10plus.de/DB=1.28/CMD?ACT=SRCHA&IKT=8079&TRM=%27',vd17_id,'%27","',vd17_id,'")')))
my_data_frames_2 <- list(genre_fbs_cat3_link,genres_number_fbs_cat3,genres_members_fbs_cat3)

fbs_dedicatees_genre_society_related<- gs4_create(
  "fbs_dedicatees_genre_society_related",
  sheets = my_data_frames_1)

fbs_dedicatees_genre_neutral_NA<- gs4_create(
  "fbs_dedicatees_genre_neutral_NA",
  sheets = my_data_frames_2)

fbs_dedicatees_genre_society_related

fbs_dedicatees_genre_neutral_NA

```
