---
title: "FBS analysis"
output:
  html_notebook:
    code_folding: hide
    toc: yes
---

```{r setup,echo=F}
knitr::opts_knit$set(root.dir = here::here())
library(here)
source(here("code/common_basis.R"), local = knitr::knit_global())
library(tidyverse)
library(gghsci)
library(gt)
p <- function(number) {
  return(format(number, scientific = FALSE, big.mark = ","))
}
pp <- function(percentage, accuracy = 0.01) {
  return(scales::percent(percentage, accuracy = accuracy))
}
```

```{r}
list_rescue <- c("Palmen Orden", "Palmen-Orden", "Palmenorden", "Fruchtbringend", "Frucht-bringend", "Frucht Bringend", "Die deutsche Akademie des 17. Jahrhunderts - Fruchtbringende Gesellschaft", "Akademie des 17. Jahrhunderts", "Akademie des Siebzehnten Jahrhunderts", "Deutsche Akademie des Siebzehnten Jahrhunderts", "Deutsche Akademie des 17. Jahrhunderts", "Palmenorden", "Akademie des Siebzehnten Jahrhunderts", "Akademie des 17. Jahrhunderts", "Societas Fructifera", "Frugtbringende Selskab", "Fruitbearing Society", "Sociedad Fructífera", "Société des Fructifiants", "Ordre du Palmier", "Società dei Carpofori", "Towarzystwo Owocodajne", "Komunitas Fruitbearing", "Плодоносное общество", "丰收学会")

vd17_rescue <- vd17_a %>%
  mutate(value = str_replace_all(value, sql("CHR(0)"), "_")) %>%
  collect() %>%
  filter(grepl(paste(list_rescue, collapse = "|"), value)) %>%
  mutate(rescue_value = value, rescue_field = field_code) %>%
  select(record_number, rescue_value, rescue_field) %>%
  distinct()
```

```{r}
vd17_rescue_additional_field <- vd17_a %>%
  filter(field_code %in% c("029A", "029F", "029G", "028G", "037A"), subfield_code %in% c("a", "B", "P")) %>%
  select(record_number, resuce_additional_field = value)

vd17_a_rescue <- vd17_rescue %>%
  copy_to_a(con, temporary = TRUE, overwrite = TRUE) %>%
  left_join(vd17_rescue_additional_field, by = c("record_number")) %>%
  collect() %>%
  distinct()
```

```{r}
all_match <- read.csv(here("all_match.csv"))
all_match <- select(all_match, -c("X", "full_name_vd17", "normalized_year", "field_number"))
all_match_subset <- all_match %>%
  filter(
    field_code %in% c("028A", "028B", "028C"), # FBS GND has to appear in one of these fields
    is.na(role) | !role %in% c("ctb", "dte"), # normed role has to be unknown or not one of these
    is.na(role) | !(role == "oth" & field_code == "028C" & !is.na(role2) & str_detect(role2, "^Beiträger|^Mitwirkender")), # in field 028C, if role is other, role2 should not be one of these
    is.na(role2) | !str_detect(role2, !!!str_flatten(c(
      "^AdressatIn",
      "ErwähnteR",
      "GefeierteR",
      "Mitglied eines Ausschusses, der akademische Grade vergibt",
      "Normerlassende Gebietskörperschaft",
      "Praeses",
      "RespondentIn",
      "Sonstige Person, Familie und Körperschaft",
      "VerfasserIn eines Vorworts",
      "VerfasserIn von ergänzendem Text",
      "VerfasserIn von Zusatztexten",
      "VertragspartnerIn",
      "WidmendeR",
      "WidmungsempfängerIn",
      "ZensorIn"
    ), collapse = "|^"))
  )
```

```{r}
all_match_subset <- select(all_match_subset, -c("role"))
```


# Joining vd17_id with fbs_links_of_interest
```{r}
fbs_links_of_interest_local <- fbs_links_of_interest_a %>%
  inner_join(fbs_metadata_a %>% select(GND, Member_number_new, First_name_new, Last_name_new, Society_name, DOB, DOD) %>% mutate(GND = str_c("gnd/", GND))) %>%
  inner_join(vd17_id_a) %>%
  mutate(member_number = Member_number_new, first_name = First_name_new, last_name = Last_name_new) %>%
  collect() %>%
  select(where(~ !all(is.na(.x))))

fbs_links_of_interest_local <- select(fbs_links_of_interest_local, c("record_number", "vd17_id", "member_number", "first_name", "last_name", "role2", "field_code"))
```

```{r}
fbs_links_of_interest_matches <- rbind(fbs_links_of_interest_local, all_match_subset)

fbs_links_of_interest_matches <- fbs_links_of_interest_matches %>%
  distinct()

fbs_rescue <- fbs_links_of_interest_matches %>%
  merge(vd17_a_rescue, by = c("record_number"), all = TRUE) %>%
  distinct()
```

# Creating local tables of vd17 normalized years, genres, languages, id and title.
```{r}
vd17_normalized_years_local <- vd17_normalized_years_a %>%
  collect()
genre_list2 <- c("Educational", "Schul- und Hochschulschriften", "Hochschulschrift", "Dissertation", "Dissertationensammlung", "Matrikel", "Universitätsprogramm", "Vorlesung", "Vorlesungsverzeichnis", "Jugendsachbuch", "Rechenbuch", "Schulbuch", "Fibel", "Lesebuch", "Schulprogramm", "Governmental", "Amtsdruckschrift", "Edikt", "Gesetz", "Gesetzesammlung", "Kapitulation", "Mandat", "Privileg", "Richtlinie", "Verordnung", "Vertrag", "Judicial", "Legal", "Entscheidungssammlung", "Fallsammlung", "Konsiliensammlung", "Konsilium", "Satzung", "Religious", "Theological", "Agende", "Beichtspiegel", "Bibel", "Brevier", "Gebet", "Katechismus", "Missale", "Psalter", "Rituale", "Other Governmental and Institutional", "Formularsammlung", "Schreibmeisterbuch", "Regesten", "Urkundenbuch", "Business", "Mercantile", "Anzeige", "Subskriptionsanzeige", "Meßrelation", "Subskribentenliste", "Verkaufskatalog", "Antiquariatskatalog", "Auktionskatalog", "Buchhandelskatalog", "Meßkatalog", "War Related", "Festungsbau", "Kriegskunde", "General Works", "Bericht", "Brief", "Briefsammlung", "Regelsammlung", "Statistik", "Streitschrift")

vd17_parts_of_multipart_works <- vd17_parts_of_multipart_works_a %>%
  collect() %>%
  mutate(multipart = "multipart")

vd17_genres_local <- vd17_genres_a %>%
  collect() %>%
  filter(!genre %in% c(genre_list2)) %>%
  mutate(genre_full = a) %>%
  select(record_number, genre, genre_full)

vd17_normalized_langs_local <- vd17_normalized_langs_a %>%
  collect()

vd17_id_local <- vd17_id_a %>%
  collect()

vd17_titles_local <- vd17_a %>%
  filter(field_code %in% c("021A", "021G", "021M", "021N", "022A"), subfield_code %in% c("a", "d", "h")) %>%
  select(record_number, title_additional_field = value) %>%
  collect()

vd17_corporate_authors_name <- vd17_a %>%
  filter(field_code %in% c("029A", "029F", "029G"), subfield_code %in% c("a")) %>%
  mutate(corporate_subfield_code_a = field_code, name_corporate = value) %>%
  select(record_number, corporate_subfield_code_a, name_corporate) %>%
  collect()

vd17_corporate_authors_gnd <- vd17_a %>%
  filter(field_code %in% c("029A", "029F", "029G"), subfield_code %in% c("7")) %>%
  mutate(corporate_subfield_code_7 = field_code, gnd_corporate = value) %>%
  select(record_number, corporate_subfield_code_7, gnd_corporate) %>%
  collect()

vd17_corporate_authors_ppn <- vd17_a %>%
  filter(field_code %in% c("029A", "029F", "029G"), subfield_code %in% c("9")) %>%
  mutate(corporate_subfield_code_9 = field_code, ppn_corporate = value) %>%
  select(record_number, corporate_subfield_code_9, ppn_corporate) %>%
  collect()

vd17_corporate_authors_role <- vd17_a %>%
  filter(field_code %in% c("029A", "029F", "029G"), subfield_code %in% c("B")) %>%
  mutate(corporate_subfield_code_B = field_code, role_corporate = value) %>%
  select(record_number, corporate_subfield_code_B, role_corporate) %>%
  collect()

vd17_corporate_name_gnd <- merge(vd17_corporate_authors_name, vd17_corporate_authors_gnd, by = c("record_number"), all = TRUE) %>%
  distinct()
vd17_corporate_name_ppn <- merge(vd17_corporate_name_gnd, vd17_corporate_authors_ppn, by = c("record_number"), all = TRUE) %>%
  distinct()
vd17_corporate <- merge(vd17_corporate_name_ppn, vd17_corporate_authors_role, by = c("record_number"), all = TRUE) %>%
  distinct()

vd17_genres_combined <- vd17_genres_local %>%
  group_by(record_number) %>%
  mutate(combined_all_genres = toString(unique(genre_full))) %>%
  distinct(record_number, combined_all_genres)
```

```{r}
genre_list1_a <- c("Lyrik", "Poetry", "Ballade", "Elegie", "Epigramm", "Epikedeion", "Figurengedicht", "Gesangbuch", "Lied", "Kirchenlied", "Liedersammlung")
genre_list1_b <- c("Drama", "Theatre", "Fastnachtspiel", "Komödie", "Märtyrerdrama", "Schauspiel", "Schwank", "Theaterzettel", "Tragödie")
genre_list1_c <- c("Epik", "Prose", "Anekdote", "Autobiographie", "Biographie", "Epos", "Erzählung", "Erzählsammlung", "Fabel", "Märchen", "Novelle", "Reisebericht", "Roman", "Sage", "Satire", "Verserzählung")
genre_list1_d <- c("Other Literature Related", "Anthologie", "Emblembuch", "Erotische Literatur", "Kommentar", "Libretto", "Schäferdichtung")
genre_list1_e <- c("Linguistic and Language", "Grammatik", "Konkordanz", "Lexikon", "Poetik", "Rhetorik", "Wörterbuch")
genre_list1_f <- c("Virtue, Civility and Ethics", "Aphorismus", "Anstandsliteratur", "Briefsteller", "Frauenliteratur", "Fürstenspiegel", "Hausväterliteratur", "Jugendbuch", "Moralische Wochenschrift", "Spiel", "Sprichwortsammlung", "Zitatensammlung")
genre_list1_g <- c("Other Society Related", "Gelegenheitsschrift", "Gesellschaftschrift", "Akademieschrift", "Funeral Sermons", "Leichenpredigt", "Leichenpredigtsammlung")
```


```{r}
genre_list3_a <- c("History, Archaeology and related", "Archäologie", "Altertumskunde", "Chronik", "Erlebnisbericht", "Genealogie", "Tagebuch", "Wappenbuch")
genre_list3_b <- c("Botany, Zoology, Agriculture", "Botanik", "Gartenbau", "Jagdliteratur", "Landwirtschaft", "Praktik", "Pflanzenbuch", "Tierbuch", "Zoologie")
genre_list3_c <- c("Geography, Geology, Mineralogy, Mining", "Atlas", "Bergbau", "Geographie", "Geologie", "Itinerar", "Karte", "Ortsverzeichnis", "Plan", "Mineralogie", "Reiseführer", "Topographie")
genre_list3_d <- c("Mathematics, Natural Sciences, Astronomy", "Alchemie", "Astronomie", "Astrologie", "Chemie", "Physik", "Akustik", "Magnetismus", "Mechanik", "Optik", "Geometrie", "Mathematik")
genre_list3_e <- c("Medicine, Pharmacy", "Anatomie", "Arzneibuch", "Chiromantie", "Chirurgie", "Gynäkologie", "Medizin", "Pharmakopöe", "Physiognomie", "Seuchenschrift", "Tiermedizin")
genre_list3_f <- c("Music and related", "Musikbuch", "Musiknoten")
genre_list3_g <- c("Arts and related", "Architektur", "Ornamentstich")
genre_list3_h <- c("Literature, language and related", "Festbeschreibung", "Rede", "Panegyrikos", "Sprachführer")
genre_list3_i <- c("Education", "Pädagogik")
genre_list3_j <- c("Manners and customs", "Kochbuch")
genre_list3_k <- c("Religion", "Theology and related", "Ars moriendi", "Erbauungsliteratur", "Freimaurerliteratur", "Gebetbuch", "Heiligenvita", "Jesuitendrama", "Judaicum", "Legende", "Ordensliteratur", "Perioche", "Predigtsammlung", "Totentanz")
genre_list3_l <- c("General Works", "Adressbuch", "Almanach", "Anleitung", "Bibliographie", "Buchbinderanweisung", "Bücheranzeige", "Einführung", "Enzyklopädie", "Führer", "Handbuch", "Kalender", "Katalog", "Bibliothekskatalog", "Kommentar", "Konkordanz", "Musterbuch", "Ratgeber", "Porträtwerk", "Preisschrift", "Regelsammlung", "Rezension", "Rezensionszeitschrift", "Traktat", "Trivialliteratur", "Kolportageliteratur", "Volksschrifttum", "Volksbuch")
genre_list3_m <- c("Formats", "Einblattdruck", "Flugschrift", "Tabelle", "Zeitung", "Zeitschrift")
```

# The below plots depicts the genre frequency of FBS publications for Society-related genres.
```{r}
genres_fbs <- fbs_rescue %>%
  left_join(vd17_genres_local, by = c("record_number")) %>%
  select(record_number, genre, genre_full)

fbs_without_genre <- genres_fbs %>%
  filter(is.na(genres_fbs$genre))

vd17_genres_local_cat1 <- vd17_genres_local %>%
  filter(genre %in% c(genre_list1_a, genre_list1_b, genre_list1_c, genre_list1_d, genre_list1_e, genre_list1_f, genre_list1_g)) %>%
  select(record_number, genre, genre_full)

genre_na_cat1 <- rbind(fbs_without_genre, vd17_genres_local_cat1)

genres_fbs_cat1 <- fbs_rescue %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year) == 4) %>%
  left_join(genre_na_cat1, by = c("record_number")) %>%
  left_join(vd17_titles_local %>% select(record_number, title_additional_field), by = c("record_number")) %>%
  left_join(vd17_normalized_langs_local %>% select(record_number, publication_language, original_language), by = c("record_number")) %>%
  left_join(vd17_genres_combined, by = c("record_number")) %>%
  left_join(vd17_parts_of_multipart_works, by = c("record_number")) %>%
  left_join(vd17_corporate, by = c("record_number")) %>%
  select(record_number, normalized_year, vd17_id, title_additional_field, member_number, first_name, last_name, role2, field_code, original_language, publication_language, genre, genre_full, combined_all_genres, rescue_value, rescue_field, resuce_additional_field, corporate_subfield_code_a, corporate_subfield_code_7, corporate_subfield_code_9, corporate_subfield_code_B, name_corporate, gnd_corporate, ppn_corporate, role_corporate, multipart) %>%
  mutate(genre_category = case_when(
    genre %in% genre_list1_a ~ "Lyrik/Poetry",
    genre %in% genre_list1_b ~ "Drama/Theatre",
    genre %in% genre_list1_c ~ "Epik/Prose",
    genre %in% genre_list1_d ~ "Other Literature Related",
    genre %in% genre_list1_e ~ "Linguistic and Language",
    genre %in% genre_list1_f ~ "Virtue, Civility and Ethics",
    genre %in% genre_list1_g ~ "Other Society Related"
  )) %>%
  distinct()
```
```{r}
genres_number_fbs_cat1 <- genres_fbs_cat1 %>%
  select(vd17_id, record_number, normalized_year, genre, genre_full) %>%
  distinct(vd17_id, record_number, normalized_year, genre, genre_full) %>%
  group_by(record_number, normalized_year) %>%
  count(genre_full, genre) %>%
  arrange(desc(n)) %>%
  mutate(genre_category = case_when(
    genre %in% genre_list1_a ~ "Lyrik/Poetry",
    genre %in% genre_list1_b ~ "Drama/Theatre",
    genre %in% genre_list1_c ~ "Epik/Prose",
    genre %in% genre_list1_d ~ "Other Literature Related",
    genre %in% genre_list1_e ~ "Linguistic and Language",
    genre %in% genre_list1_f ~ "Virtue, Civility and Ethics",
    genre %in% genre_list1_g ~ "Other Society Related"
  ))


genres_number_fbs_cat1 %>%
  ggplot(aes(x = normalized_year, y = n, fill = genre_category)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~genre_category, scales = "free_y") +
  xlab("Year") +
  ylab("All_FBS-Society-related genres") +
  scale_x_continuous(breaks = seq(1000, 2000, by = 5)) +
  theme_hsci_discrete() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

# Genre frequency of FBS publications by year per author for Society-related genres.
```{r}
genres_members_fbs_cat1 <- genres_fbs_cat1 %>%
  select(vd17_id, record_number, normalized_year, member_number, genre, genre_full) %>%
  distinct(vd17_id, record_number, normalized_year, member_number, genre, genre_full) %>%
  group_by(normalized_year, member_number) %>%
  count(genre_full, genre) %>%
  arrange(desc(n)) %>%
  mutate(genre_category = case_when(
    genre %in% genre_list1_a ~ "Lyrik/Poetry",
    genre %in% genre_list1_b ~ "Drama/Theatre",
    genre %in% genre_list1_c ~ "Epik/Prose",
    genre %in% genre_list1_d ~ "Other Literature Related",
    genre %in% genre_list1_e ~ "Linguistic and Language",
    genre %in% genre_list1_f ~ "Virtue, Civility and Ethics",
    genre %in% genre_list1_g ~ "Other Society Related"
  ))
```

# The below plots depicts the genre frequency of FBS publications for Neutral genres.
```{r}
vd17_genres_local_cat3 <- vd17_genres_local %>%
  filter(genre %in% c(genre_list3_a, genre_list3_b, genre_list3_c, genre_list3_d, genre_list3_e, genre_list3_f, genre_list3_g, genre_list3_h, genre_list3_i, genre_list3_j, genre_list3_k, genre_list3_l, genre_list3_m)) %>%
  select(record_number, genre, genre_full)

genre_na_cat3 <- rbind(fbs_without_genre, vd17_genres_local_cat3)

genres_fbs_cat3 <- fbs_rescue %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year) == 4) %>%
  left_join(genre_na_cat3, by = c("record_number")) %>%
  left_join(vd17_titles_local %>% select(record_number, title_additional_field), by = c("record_number")) %>%
  left_join(vd17_normalized_langs_local %>% select(record_number, publication_language, original_language), by = c("record_number")) %>%
  left_join(vd17_genres_combined, by = c("record_number")) %>%
  left_join(vd17_parts_of_multipart_works, by = c("record_number")) %>%
  left_join(vd17_corporate, by = c("record_number")) %>%
  select(record_number, normalized_year, vd17_id, title_additional_field, member_number, first_name, last_name, role2, field_code, original_language, publication_language, genre, genre_full, combined_all_genres, rescue_value, rescue_field, resuce_additional_field, corporate_subfield_code_a, corporate_subfield_code_7, corporate_subfield_code_9, corporate_subfield_code_B, name_corporate, gnd_corporate, ppn_corporate, role_corporate, multipart) %>%
  mutate(genre_category = case_when(
    genre %in% genre_list3_a ~ "History, Archaeology and related",
    genre %in% genre_list3_b ~ "Botany, Zoology, Agriculture",
    genre %in% genre_list3_c ~ "Geography, Geology, Mineralogy, Mining",
    genre %in% genre_list3_d ~ "Mathematics, Natural Sciences, Astronomy",
    genre %in% genre_list3_e ~ "Medicine, Pharmacy",
    genre %in% genre_list3_f ~ "Music and related",
    genre %in% genre_list3_g ~ "Arts and related",
    genre %in% genre_list3_h ~ "Literature, language and related",
    genre %in% genre_list3_i ~ "Education",
    genre %in% genre_list3_j ~ "Manners and customs",
    genre %in% genre_list3_k ~ "Religion/Theology and related",
    genre %in% genre_list3_l ~ "General works",
    genre %in% genre_list3_m ~ "Formats"
  )) %>%
  distinct()
```
```{r}
genres_number_fbs_cat3 <- genres_fbs_cat3 %>%
  select(vd17_id, record_number, normalized_year, genre, genre_full) %>%
  distinct(vd17_id, record_number, normalized_year, genre, genre_full) %>%
  group_by(normalized_year) %>%
  count(genre, genre_full) %>%
  arrange(desc(n)) %>%
  mutate(genre_category = case_when(
    genre %in% genre_list3_a ~ "History, Archaeology and related",
    genre %in% genre_list3_b ~ "Botany, Zoology, Agriculture",
    genre %in% genre_list3_c ~ "Geography, Geology, Mineralogy, Mining",
    genre %in% genre_list3_d ~ "Mathematics, Natural Sciences, Astronomy",
    genre %in% genre_list3_e ~ "Medicine, Pharmacy",
    genre %in% genre_list3_f ~ "Music and related",
    genre %in% genre_list3_g ~ "Arts and related",
    genre %in% genre_list3_h ~ "Literature, language and related",
    genre %in% genre_list3_i ~ "Education",
    genre %in% genre_list3_j ~ "Manners and customs",
    genre %in% genre_list3_k ~ "Religion/Theology and related",
    genre %in% genre_list3_l ~ "General works",
    genre %in% genre_list3_m ~ "Formats"
  ))


genres_number_fbs_cat3 %>%
  ggplot(aes(x = normalized_year, y = n, fill = genre_category)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~genre_category, scales = "free_y") +
  xlab("Year") +
  ylab("All_FBS-Genre_Neutral_genres") +
  scale_x_continuous(breaks = seq(1000, 2000, by = 5)) +
  theme_hsci_discrete() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```
# Genre frequency of FBS publications by year per author for Neutral genres.
```{r}
genres_members_fbs_cat3 <- genres_fbs_cat3 %>%
  select(vd17_id, record_number, normalized_year, member_number, genre, genre_full) %>%
  distinct(vd17_id, record_number, normalized_year, member_number, genre, genre_full) %>%
  group_by(normalized_year, member_number) %>%
  count(genre_full, genre) %>%
  arrange(desc(n)) %>%
  mutate(genre_category = case_when(
    genre %in% genre_list3_a ~ "History, Archaeology and related",
    genre %in% genre_list3_b ~ "Botany, Zoology, Agriculture",
    genre %in% genre_list3_c ~ "Geography, Geology, Mineralogy, Mining",
    genre %in% genre_list3_d ~ "Mathematics, Natural Sciences, Astronomy",
    genre %in% genre_list3_e ~ "Medicine, Pharmacy",
    genre %in% genre_list3_f ~ "Music and related",
    genre %in% genre_list3_g ~ "Arts and related",
    genre %in% genre_list3_h ~ "Literature, language and related",
    genre %in% genre_list3_i ~ "Education",
    genre %in% genre_list3_j ~ "Manners and customs",
    genre %in% genre_list3_k ~ "Religion/Theology and related",
    genre %in% genre_list3_l ~ "General works",
    genre %in% genre_list3_m ~ "Formats"
  ))
```
# Creating fbs with NA genres
```{r}
genre_fbs_ <- fbs_rescue %>%
  left_join(vd17_genres_local, by = c("record_number"))

fbs_with_no_genre <- genre_fbs_ %>%
  filter(is.na(genre)) %>%
  distinct()

fbs_no_genre <- fbs_with_no_genre %>%
  left_join(vd17_normalized_years_local, by = c("record_number")) %>%
  filter(normalized_year >= 1600, normalized_year <= 1700) %>%
  filter(nchar(normalized_year) == 4) %>%
  left_join(vd17_titles_local %>% select(record_number, title_additional_field), by = c("record_number")) %>%
  left_join(vd17_normalized_langs_local %>% select(record_number, publication_language, original_language), by = c("record_number")) %>%
  left_join(vd17_parts_of_multipart_works, by = c("record_number")) %>%
  left_join(vd17_corporate, by = c("record_number")) %>%
  select(record_number, normalized_year, vd17_id, title_additional_field, member_number, first_name, last_name, role2, field_code, original_language, publication_language, genre, rescue_value, rescue_field, resuce_additional_field, corporate_subfield_code_a, corporate_subfield_code_7, corporate_subfield_code_9, corporate_subfield_code_B, name_corporate, gnd_corporate, ppn_corporate, role_corporate, multipart)
```
# Solving the Token_authontication problem
```{r}
options(gargle_oauth_cache = ".secrets")

# Authenticate manually

gs4_auth()

# If successful, the previous step stores a token file.

# Check that a file has been created with:

list.files(".secrets/")

# Check that the non-interactive authentication works by first deauthorizing:

gs4_deauth()

# Authenticate using token. If no browser opens, the authentication works.

gs4_auth(cache = ".secrets", email = "narges.azizifard@gmail.com")
```

# Creating the google spreadsheet
```{r}
my_data_frames_1 <- list(genres_fbs_cat1, genres_number_fbs_cat1, genres_members_fbs_cat1)

my_dataframes_2 <- list(genres_fbs_cat3, genres_number_fbs_cat3, genres_members_fbs_cat3, fbs_no_genre)

fbs_publications_genre_society_related <- gs4_create(
  "fbs_publications_genre_society_related",
  sheets = my_data_frames_1
)

fbs_publications_genre_neutral_NA <- gs4_create(
  "fbs_publications_genre_neutral_NA",
  sheets = my_dataframes_2
)

fbs_publications_genre_society_related

fbs_publications_genre_neutral_NA
```
