---
title: "VD17 analysis"
output:
  html_notebook:
    code_folding: hide
    toc: yes
---

```{r setup,echo=F}
knitr::opts_knit$set(root.dir = here::here())
source(here::here("code/common_basis.R"), local = knitr::knit_global())
```


# Overall summary

VD17 has `r p(vd17_a %>% distinct(record_number) %>% count() %>% pull(n))` records in total.

## Field code usage overview

```{r field_code_usage_overview}
vd17_field_code_usage_stats <- vd17_c %>%
  group_by(field_code) %>%
  summarize(records = n_distinct(record_number), n = n(), .groups = "drop") %>%
  compute() %>%
  left_join(
    vd17_a %>%
      inner_join(in_fbs) %>%
      group_by(field_code) %>%
      summarize(fbs_records = n_distinct(record_number), fbs_n = n(), .groups = "drop")
  ) %>%
  mutate(vals_per_rec = n / records, vals_per_fbs_rec = fbs_n / fbs_records) %>%
  left_join(
    vd17_c %>%
      count(record_number, field_code) %>%
      filter(n > 1L) %>%
      ungroup() %>%
      count(field_code, name = "recs_with_mult_vals") %>%
      compute()
  ) %>%
  left_join(
    vd17_a %>%
      inner_join(in_fbs) %>%
      count(record_number, field_code) %>%
      filter(n > 1L) %>%
      ungroup() %>%
      count(field_code, name = "fbs_recs_with_mult_vals")
  ) %>%
  arrange(field_code) %>%
  replace_na(list(fbs_records = 0, fbs_n = 0, recs_with_mult_vals = 0, fbs_recs_with_mult_vals = 0)) %>%
  compute()
```

In total, `r p(vd17_field_code_usage_stats %>% count() %>% pull(n))` distinct PICA+ fields are used in VD17.

```{r field_code_usage_overview_table}
vd17_field_code_usage_stats %>%
  mutate(field_code = str_c('<a name="', field_code, '"></a>', field_code)) %>%
  gt() %>%
  fmt_number(where(is.numeric), decimals = 0) %>%
  fmt_number(vals_per_rec, decimals = 2, drop_trailing_zeros = TRUE) %>%
  fmt_number(vals_per_fbs_rec, decimals = 2, drop_trailing_zeros = TRUE) %>%
  fmt_markdown(field_code)
```

## Field code usage overview by subfield

```{r field_subfield_code_usage_overview}
vd17_subfield_code_example_vals <- vd17_c %>%
  distinct(field_code, subfield_code, value) %>%
  compute() %>%
  group_by(field_code, subfield_code) %>%
  slice_sample(n = 7) %>%
  summarize(e_vals = str_flatten(value, collapse = "|"), .groups = "drop") %>%
  compute()

vd17_subfield_code_dist_vals <- vd17_c %>%
  distinct(field_code, subfield_code, value) %>%
  count(field_code, subfield_code, name = "dist_vals") %>%
  compute()

vd17_subfield_code_usage_stats <- vd17_c %>%
  group_by(field_code, subfield_code) %>%
  summarize(records = n_distinct(record_number), n = n(), .groups = "drop") %>%
  compute() %>%
  left_join(
    vd17_a %>%
      inner_join(in_fbs) %>%
      group_by(field_code, subfield_code) %>%
      summarize(fbs_records = n_distinct(record_number), fbs_n = n(), .groups = "drop")
  ) %>%
  mutate(vals_per_rec = n / records, vals_per_fbs_rec = fbs_n / fbs_records) %>%
  left_join(
    vd17_c %>%
      count(record_number, field_code, subfield_code) %>%
      filter(n > 1L) %>%
      ungroup() %>%
      count(field_code, subfield_code, name = "recs_with_mult_vals") %>%
      compute()
  ) %>%
  left_join(
    vd17_a %>%
      inner_join(in_fbs) %>%
      count(record_number, field_code, subfield_code) %>%
      filter(n > 1L) %>%
      ungroup() %>%
      count(field_code, subfield_code, name = "fbs_recs_with_mult_vals")
  ) %>%
  replace_na(list(fbs_records = 0, fbs_n = 0, recs_with_mult_vals = 0, fbs_recs_with_mult_vals = 0)) %>%
  left_join(vd17_subfield_code_dist_vals, by = c("field_code", "subfield_code")) %>%
  left_join(vd17_subfield_code_example_vals, by = c("field_code", "subfield_code")) %>%
  relocate(field_code, subfield_code, records, dist_vals, e_vals) %>%
  arrange(field_code, subfield_code) %>%
  compute()

rm(vd17_subfield_code_example_vals, vd17_subfield_code_dist_vals)
```

In total, `r p(vd17_subfield_code_usage_stats %>% count() %>% pull(n))` distinct PICA+ field+subfield combinations are used in VD17.

```{r subfield_code_usage_overview_table}
vd17_subfield_code_usage_stats %>%
  mutate(subfield_code = str_c('<a name="', field_code, "$", subfield_code, '"></a>', field_code, "$", subfield_code)) %>%
  gt(groupname_col = "field_code") %>%
  fmt_number(where(is.numeric), decimals = 0) %>%
  fmt_number(vals_per_rec, decimals = 2, drop_trailing_zeros = TRUE) %>%
  fmt_number(vals_per_fbs_rec, decimals = 2, drop_trailing_zeros = TRUE) %>%
  fmt_markdown(subfield_code)
```

```{r}
library(googlesheets4)
#
# gs4_create(name = "vd17_field_usage", sheets = list("field_code"=vd17_field_code_usage_stats,"subfield_code"=vd17_subfield_code_usage_stats))
# write_sheet(vd17_field_code_usage_stats,ss="1brWclkuD3PwXmDei4dkYaWzxXIN_19hVy_PkfAwrctk",sheet="field_code")
# write_sheet(vd17_subfield_code_usage_stats,ss="1brWclkuD3PwXmDei4dkYaWzxXIN_19hVy_PkfAwrctk",sheet="subfield_code")
```

# Temporal overview

## Overall

```{r}
vd17_c %>%
  filter(field_code == "011@", subfield_code == "a") %>%
  mutate(year = as.integer(value)) %>%
  filter(year >= 1600, year <= 1700) %>%
  collect() %>%
  left_join(in_fbs) %>%
  replace_na(list(in_fbs = FALSE)) %>%
  mutate(in_fbs = if_else(in_fbs, "FBS", "VD17"), in_fbs = fct_relevel(in_fbs, "VD17")) %>%
  ggplot(aes(x = year, fill = in_fbs)) +
  geom_bar(width = 1) +
  labs(fill = NULL) +
  scale_x_continuous(breaks = seq(1000, 2000, by = 20)) +
  scale_y_continuous(breaks = seq(0, 10000, by = 500)) +
  theme_hsci_discrete() +
  theme(legend.justification = c(0, 1), legend.position = c(0.02, 0.98), legend.background = element_blank(), legend.box.just = "bottom", legend.key = element_blank(), legend.box = "horizontal")
```

## By genre

### VD17 as a whole

#### Absolute

```{r}
vd17_c %>%
  filter(field_code == "044S", subfield_code == "9") %>%
  collect() %>%
  left_join(
    vd17_044s_raw %>%
      filter(field_code == "150") %>%
      select(genre = value, value = ppn) %>%
      mutate(genre = str_replace_all(genre, ":.*", "")) %>%
      collect(),
    by = c("value")
  ) %>%
  select(record_number, genre) %>%
  left_join(vd17_c %>%
    filter(field_code == "011@", subfield_code == "a") %>%
    select(record_number, year = value) %>%
    mutate(year = as.integer(year)) %>%
    filter(year >= 1600, year <= 1700) %>%
    collect(),
  by = c("record_number")
  ) %>%
  mutate(genre = fct_lump_n(genre, 12)) %>%
  ggplot(aes(x = year, fill = genre)) +
  geom_bar(width = 1) +
  labs(fill = NULL) +
  scale_x_continuous(breaks = seq(1000, 2000, by = 20)) +
  scale_y_continuous(breaks = seq(0, 10000, by = 500)) +
  theme_hsci_discrete() +
  theme(legend.position = "bottom")
```

#### Proportional

```{r}
vd17_c %>%
  filter(field_code == "044S", subfield_code == "9") %>%
  collect() %>%
  left_join(vd17_044s_raw %>%
    filter(field_code == "150") %>%
    select(genre = value, value = ppn) %>%
    collect(),
  by = c("value")
  ) %>%
  mutate(genre = str_replace(genre, ":.*", "")) %>%
  select(record_number, genre) %>%
  left_join(vd17_c %>%
    filter(field_code == "011@", subfield_code == "a") %>%
    select(record_number, year = value) %>%
    mutate(year = as.integer(year)) %>%
    filter(year >= 1600, year <= 1700) %>%
    collect(),
  by = c("record_number")
  ) %>%
  mutate(genre = fct_lump_n(genre, 12)) %>%
  ggplot(aes(x = year, fill = genre)) +
  geom_bar(width = 1, position = "fill") +
  labs(fill = NULL) +
  scale_x_continuous(breaks = seq(1000, 2000, by = 20)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.1)) +
  theme_hsci_discrete() +
  theme(legend.position = "bottom")
```

### FBS subset

#### Absolute

```{r}
fbs_a %>%
  filter(field_code == "044S", subfield_code == "9") %>%
  left_join(vd17_044s_raw %>%
    filter(field_code == "150") %>%
    select(genre = value, value = ppn),
  by = c("value")
  ) %>%
  mutate(genre = str_replace_all(genre, ":.*", "")) %>%
  select(record_number, genre) %>%
  left_join(fbs_a %>%
    filter(field_code == "011@", subfield_code == "a") %>%
    select(record_number, year = value) %>%
    mutate(year = as.integer(year)) %>%
    filter(year >= 1600, year <= 1700),
  by = c("record_number")
  ) %>%
  count(year, genre) %>%
  ungroup() %>%
  collect() %>%
  mutate(genre = fct_lump_n(genre, 11, w = n)) %>%
  group_by(year, genre) %>%
  summarize(n = sum(n), .groups = "drop") %>%
  complete(year, genre, fill = list(n = 0)) %>%
  ggplot(aes(x = year, y = n)) +
  geom_step() +
  labs(fill = NULL) +
  scale_x_continuous(breaks = seq(1000, 2000, by = 40)) +
  theme_hsci_discrete() +
  theme(legend.position = "bottom") +
  facet_wrap(~genre, scales = "free_y")
```

#### Proportional

```{r}
fbs_a %>%
  filter(field_code == "044S", subfield_code == "9") %>%
  left_join(vd17_044s_raw %>%
    filter(field_code == "150") %>%
    select(genre = value, value = ppn),
  by = c("value")
  ) %>%
  mutate(genre = str_replace_all(genre, ":.*", "")) %>%
  select(record_number, genre) %>%
  left_join(fbs_a %>%
    filter(field_code == "011@", subfield_code == "a") %>%
    select(record_number, year = value) %>%
    mutate(year = as.integer(year)) %>%
    filter(year >= 1600, year <= 1700),
  by = c("record_number")
  ) %>%
  count(year, genre) %>%
  ungroup() %>%
  collect() %>%
  mutate(genre = fct_lump_n(genre, 12, w = n)) %>%
  group_by(year, genre) %>%
  summarize(n = sum(n), .groups = "drop") %>%
  complete(year, genre, fill = list(n = 0)) %>%
  ggplot(aes(x = year, y = n, fill = genre)) +
  geom_col(width = 1, position = "fill") +
  labs(fill = NULL) +
  scale_x_continuous(breaks = seq(1000, 2000, by = 20)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.1)) +
  theme_hsci_discrete() +
  theme(legend.position = "bottom")
```
